A performance assessment of evolutionary algorithms in volunteer computing environments: the importance of entropy

### 2016-11-13 EvoPar2017/paper.Rnw
Reviewed state of the art
Someone like @mariosky should try to review this, maybe adding a bit more. EvoStar allows up to 16 pages.

Volunteer computing involves a user running a program voluntarily
and, as such, has been deployed in many different ways from the
beginning of the Internet, starting with the SETI@home framework for
processing extraterrestrial signals \cite{david-seti:home}. However
the dual facts of the introduction of JavaScript as a universal language for the
browser and the browser itself as an ubiquitous web and Internet client has
made this combination the most popular for volunteer computing
frameworks such as the one we are using here, and whose first version
was described in \cite{DBLP:conf/gecco/GuervosG15}.

JavaScript can be used for either unwitting
\cite{unwitting-ec,boldrin2007distributed} or volunteer 
\cite{langdon:2005:metas,gecco07:workshop:dcor} distributed
evolutionary computation and it has been used ever since by several
authors, including more recent efforts
\cite{duda2013distributed,DBLP:journals/corr/abs-0801-1210,EvoStar2014:jsEO}.

In general, those papers go no further than a proof of concept,
attempting to gauge how many users join the effort and also how long
would it take for a concrete amount of users to reach the solution. In
general, they do not try to assess the performance of the algorithm
itself in the precise conditions they find in a volunteer computing
system, although papers such as the one by Laredo et
al. \cite{churn08:ijhpsa}, using models, try to find out the resulting
performance when the users are changing continuously according to a
Weibull distribution. In the case of Klein and Spector \cite{unwitting-ec}, the algorithm
is actually run on the server, using the browser mainly for fitness
evaluation so no actual contribution to the evaluation of the
evolutionary algorithm itself is made.

>>>>

Volunteer computing involves users deciding to run a program that acts
as a client or as a peer in an experiment
and, as such, has been deployed in many different ways from the
beginning of the Internet, starting with the SETI@home framework for
processing extraterrestrial signals \cite{david-seti:home}. However
the dual facts of the introduction of JavaScript as a universal language for the
browser and the browser itself as an ubiquitous web and Internet client has
made this combination the most popular for volunteer computing
frameworks such as the one we are using here, and whose first version
was described in [citation hidden]. 
%\cite{DBLP:conf/gecco/GuervosG15}.

Several authors have already described system using JavaScript  either
for unwitting
\cite{unwitting-ec,boldrin2007distributed} or volunteer 
\cite{langdon:2005:metas,gecco07:workshop:dcor} distributed
evolutionary computation and it has been used ever since by several
authors, including more recent efforts
\cite{duda2013distributed,DBLP:journals/corr/abs-0801-1210,EvoStar2014:jsEO}. Most
of these papers focused on testing the system by itself as proofs of
concepts, more than on its performance or their actual influence on
the result of an evolutionary algorithm. In fact, some of them do not
even work in as a distributed computing system
\cite{EvoStar2014:jsEO}, describing the expressive capabilities of
JavaScript for evolutionary computation.

The proof of concepts described above do not go further than trying to
find out  how many users join the effort and how many the system is
able to support. In fact, systems described in
\cite{gecco07:workshop:dcor} had serious scaling issues; some of them
also tried to find out how much time was needed to find the solution
or, alternatively, how many users would be needed to be competitive
with single-user single-computer implementations of the same
algorithm. However, the latest systems try to enphasize the seamless
integration of peer and volunteer computing systems \cite{leclerc2016seamless}.

This latest system offloads evaluation to browsers so the actual
algorithm runs in some other place; in general, most researchers do
not try to assess the performance of the algorithm 
itself in the precise conditions they find in a volunteer computing
system, although papers such as the one by Laredo et
al. \cite{churn08:ijhpsa}, using models, try to find out the resulting
performance when the users are changing continuously according to a
Weibull distribution. In the case of Klein and Spector \cite{unwitting-ec}, the algorithm
is actually run on the server, using the browser mainly for fitness
evaluation so no actual contribution to the evaluation of the
evolutionary algorithm itself is made.
